Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
clearer todo notes

\todo[inline]{Alessandro: please write out proof that checking only the corner cases is valid for the safety verification}

@@

\todo[inline]{Alessandro: please can we have the proof for the completeness threshold here}
\missingfigure{picture for completeness threshold}

>>>>

\todo[inline]{please will Alessandro write out the proof that checking only the corner cases is valid for the safety verification - EP}

@@

\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
\missingfigure{picture for completeness threshold}
